On Verification Patterns for Low-Level Systems via Modal Abstractions

### 2025-09-12 paper.tex
+

Conventionally, a Kripke model with its constituent must be picked. Gordon give a Kripke model for an actor-based hybrid modal logic ~\cite{} in which the transition relation is indexed by a particular command and a particular actor. Wagner et.al. takes the similar approach for the design of their program logic for reference counted memory.

The underlying model for \textsf{Iris}~\cite{jung2018iris} would be a collection of \textsc{CMRA}s ---
an algebraic cousin of a BI-algebra~\cite{ohearn1999bunched}.
This is the case for \textsf{Iris}'s one built-in modality for step-indexing~\cite{nakano-00}.
However in general, many modalities can be given proof-theoretic semantics directly within a logic. 
This is the case for \textsf{Iris}'s weakest precondition modality (which is defined within the \textsf{Iris} 
logic itself) , as well as for a wide range of other modalities in the 
literature~\cite{restall2002introduction}. These modalities are typically multi-modal, 
with a form of roughly $M~\overline{ctxt}~\phi\triangleq\ldots\rightarrow \phi~\overline{ctxt}$. 
\paragraph{Shallow Modalities in Iris Separation Logic}
\label{sec:modal_in_iris}
In a substructural setting~\cite{restall1993modalities,krebbers2017essence} the implication $\rightarrow$ 
is typically replaced with substructural implication $\sepimp$.

>>>>

Conventionally, a Kripke model with its constituent must be picked. Gordon give a Kripke model for an actor-based hybrid modal logic ~\cite{gordon2019modal} in which the transition relation is indexed by a particular command and a particular actor. Wagner et.al. takes the similar approach for the design of their program logic for reference counted memory.

On the other hand, program logics such as \textsf{Iris}~\cite{jung2018iris} utilizes Kripke model in ordering the separation algebras (a collection of \textsc{CMRA}s as an algebraic cousin of a BI-algebra~\cite{ohearn1999bunched}) both by heap extension and step index. 
This is the case for \textsf{Iris}'s one built-in modality for step-indexing~\cite{nakano-00}.
However in general, many modalities can be given proof-theoretic semantics directly within a logic. 
This is the case for \textsf{Iris}'s weakest precondition modality (which is defined within the \textsf{Iris} 
logic itself) , as well as for a wide range of other modalities in the 
literature~\cite{restall2002introduction}. These modalities are typically multi-modal, 
with a form of roughly $M~\overline{ctxt}~\phi\triangleq\ldots\rightarrow \phi~\overline{ctxt}$.

\paragraph{Shallow Modalities in Separation Logic}
\label{sec:modal_in_iris}
In a substructural setting~\cite{restall1993modalities,krebbers2017essence} the implication $\rightarrow$ 
is typically replaced with substructural implication $\sepimp$.
